Current State of Knowledge Representation Systems for Robotics

### 2011-11-22 paper.tex
Added first content for NKLR

>>>>

\subsection{NKRL}
\label{sect|nkrl}

\emph{NKRL} stands for \emph{Narrative Knowledge Representation Language}.
While this language is developped since a long time by Zarri~\cite{Zarri1997,
Zarri2008}, recent research direction include application to the robotic
field~\cite{Sabri2011}. NKRL is not {\it per-se} a knowledge representation
system, as it is primarily a language. However, it is used as the
representation and reasoning mechanism for robots by Sabri et al.

\subsubsection{Intrinsic language features}
\label{sect|nkrl-intrinsic-features}

\paragraph{Expressiveness}

\subsubsection{Integration with physical world and in the robot architecture}
\label{sect|nkrl-integration}

...seem to be mostly WIP...
